\documentclass{article}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,
	urlcolor=cyan,
}

\title{Testing Policy Document}
\author{devs101}


\begin{document}

\maketitle
\newpage

\section{Reasons for Testing}
We aim to use regular testing to ensure code quality and performance, and to ensure that the software fulfils its requirements.
We firmly believe that testing is one of the most important parts of software development, and that good testing leads to even
better software.

\section{Test Process}
In order to make testing easier and more effective, we are using Travis CI to run automated tests. Firstly, the code is linted
to ensure no syntax or semantic errors, and to ensure it follows the ECMAScript 6 standards. Then, automated unit tests are done
on all of our software modules, to ensure that there are no errors, and that the code performs as intended.
Our test reports can be found on our Travis CI profile at \url{https://travis-ci.org/dolan212/devs101}. 

\section{Test Evaluation}
If a problem is found during testing, we will allocate a team member to fix it as soon as possible. This is to ensure that all
problems are fixed in a timely fashion. We aim to ensure that there are no outstanding high severity faults before the product is released.
Travis CI is set up to automatically update the commit with the test result, and notify us on Slack, so faults are picked up as soon as
they occur.

\section{Test Process Improvement}
We will discuss the test process and all the existing tests on a regular basis, to determine if there are any improvements that need to be made.


\end{document}
